Position Paper: Against Spurious Understanding---Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-02-01 main.tex
appendix

\includegraphics[width=1.0\textwidth]{results/figures/pca_yield.png}[tb]

@@

\includegraphics[width=1.0\textwidth]{results/figures/dl.png}[tb]

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_CPI (n_pc=128).png}[tb]

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_CPI (n_pc=128).png}[tb]

@@

\caption{\label{fig-cpi}Average performance measures across folds for the CPI for the train and test set compared against the baseline autoregressive model. Shaded areas show the variation across folds.}

>>>>

\includegraphics[width=1.0\textwidth]{results/figures/pca_yield.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/dl.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_CPI (n_pc=128).png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/measures_CPI (n_pc=128).png}

@@

\caption{\label{fig-cpi-b}Average performance measures across folds for the CPI for the train and test set compared against the baseline autoregressive model. Shaded areas show the variation across folds.}

% ---------- PPI ----------

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_PPI (n_pc=128).png}

\caption{\label{fig-ppi}Average performance measures across folds for the PPI for the train and test set.}

\includegraphics[width=1.0\textwidth]{results/figures/measures_PPI (n_pc=128).png}

\caption{\label{fig-ppi-b}Average performance measures across folds for the PPI for the train and test set compared against the baseline autoregressive model. Shaded areas show the variation across folds.}

% ---------- UST (1 Mo)  ----------

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST (1 Mo) (n_pc=128).png}

\caption{\label{fig-ust-1}Average performance measures across folds for the UST (1 Mo) for the train and test set.}

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST (1 Mo).png}

\caption{\label{fig-ust-1-b}Average performance measures across folds for the UST (1 Mo) for the train and test set compared against the baseline autoregressive model. Shaded areas show the variation across folds.}

% ---------- UST (1 Yr)  ----------

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST (1 Yr) (n_pc=128).png}

\caption{\label{fig-ust-1y}Average performance measures across folds for the UST (1 Yr) for the train and test set.}

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST (1 Yr).png}

\caption{\label{fig-ust-1y-b}Average performance measures across folds for the UST (1 Yr) for the train and test set compared against the baseline autoregressive model. Shaded areas show the variation across folds.}

% ---------- UST (10 Yr)  ----------

\includegraphics[width=1.0\textwidth]{results/figures/measures_probe_UST (10 Yr) (n_pc=128).png}

\caption{\label{fig-ust-10}Average performance measures across folds for the UST (1 Yr) for the train and test set.}

\includegraphics[width=1.0\textwidth]{results/figures/measures_UST (10 Yr).png}

\caption{\label{fig-ust-10-b}Average performance measures across folds for the UST (10 Yr) for the train and test set compared against the baseline autoregressive model. Shaded areas show the variation across folds.}
